---
title: "Technical Appendix: Abstract-to-Publication Matching Pipeline"
subtitle: "Supplement to: Publication Rate of Oral Presentations at the AAGL Global Congress, 2012-2023"
author: "Tyler Muffly, MD"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(readr); library(dplyr); library(here); library(knitr)

d <- read_csv(here("output", "abstracts_with_matches.csv"), show_col_types = FALSE)
strat <- read_csv(here("output", "aim4_strategy_performance.csv"), show_col_types = FALSE)
val <- read_csv(here("output", "validation_metrics.csv"), show_col_types = FALSE)
s <- read_csv(here("output", "sensitivity_analyses.csv"), show_col_types = FALSE)
cox <- read_csv(here("output", "aim2b_cox_regression.csv"), show_col_types = FALSE)
ph <- read_csv(here("output", "cox_ph_assumption.csv"), show_col_types = FALSE)

cfg <- yaml::read_yaml(here("config.yml"))

n_total <- nrow(d)
n_congresses <- length(unique(d$congress_year))
yr_min <- min(d$congress_year)
yr_max <- max(d$congress_year)
n_definite <- sum(d$classification == "definite")
n_probable <- sum(d$classification == "probable")

xml_cache <- length(list.files(here("data", "cache", "pubmed_xml")))
html_cache <- length(list.files(here("data", "cache", "sd_html")))
```

## A1. Pipeline Architecture

The abstract-to-publication matching pipeline is implemented as a modular, fully reproducible R codebase comprising 20 R scripts, 12 test files (`r 391` unit and semantic tests), and a Shiny web application for human adjudication. The pipeline executes in 10 sequential steps, with checkpoint-based resume support for API-dependent stages. All source code and deidentified output data are available at https://github.com/mufflyt/abstract_lifetime.

### A1.1 System Requirements

- R version `r paste(R.version$major, R.version$minor, sep = ".")`
- 22 R packages (tidyverse core, rentrez, xml2, httr, jsonlite, survival, gender, shiny, bslib, googlesheets4)
- Disk cache: `r xml_cache` PubMed XML files, `r html_cache` ScienceDirect HTML files
- External APIs: NCBI E-Utilities (PubMed), CrossRef, Europe PMC, OpenAlex, Semantic Scholar, genderize.io
- Runtime: approximately 3-4 hours for a full pipeline execution on `r n_total` abstracts

### A1.2 Pipeline Steps

| Step | Script | Description | Checkpoint |
|------|--------|-------------|------------|
| 1 | `01b_parse_web.R` | Scrape JMIG supplement TOC + individual article pages from ScienceDirect | HTML cache |
| 1d | `01d_tag_session_type.R` | Walk TOC DOM to assign Oral/Video labels per abstract | - |
| 2 | `02_clean_abstracts.R` | Normalize titles/authors, extract 20+ predictor variables via NLP | - |
| 3 | `03_search_pubmed.R` | 6-strategy PubMed search per abstract via NCBI E-Utilities | RDS |
| 3b | `03b_search_crossref.R` | Supplementary search: CrossRef + Europe PMC + OpenAlex + Semantic Scholar | RDS per source |
| 3c | `03c_doi_chain_search.R` | Reverse citation search via OpenAlex (DOI-based) | RDS |
| 4 | `04_score_matches.R` | Composite scoring of all candidate publications | - |
| 5 | `05_adjudicate.R` | Apply Cochrane-aligned classification thresholds | - |
| 5b-e | `09b-d_enrich_*.R` | Publication type, author demographics, citation metrics | XML cache |
| 6 | `06_analyze_results.R` | KM, Cox PH, logistic regression, publication bias, sensitivity | - |
| 7-8 | `07/08_make_*.R` | Generate 4 tables + 9 figures | - |

## A2. Data Sources and API Usage

### A2.1 Abstract Ingestion

Conference abstracts were identified from `r n_congresses` annual JMIG supplement issues (Volume 19 Issue 6 through Volume 30 Issue 11, Supplement S). The ScienceDirect supplement listing page was scraped programmatically with polite delays (2-3 seconds between requests) and user-agent rotation. Per-article HTML was cached to disk to avoid redundant fetches on re-runs. A total of `r html_cache` article pages were cached.

Abstract text was available for congresses 2019-2023 only. Congresses 2012-2018 used an older ScienceDirect page format that did not expose structured abstract sections (Objective, Design, Setting, Patients, Intervention, Measurements, Conclusion) in the HTML. For these years, the matching algorithm relied on title and author matching without abstract-text semantic similarity.

### A2.2 Publication Search

Six complementary PubMed search strategies were applied to each abstract:

1. **Title phrase search**: first 8 significant words of the normalized title, quoted phrase in [TI] field
2. **First author search**: normalized first-author surname + initial in [1AU] field
3. **Last author search**: normalized last-author surname + initial in [LASTAU] field
4. **Author + keywords**: first author in [AU] combined with top 4 extracted keywords in [TIAB]
5. **Distinctive phrase**: 4-word distinctive phrase from the title in [TIAB]
6. **Author broad**: first author in [AU] (catch-all)

All strategies were filtered by publication date (`r cfg$default$pubmed$date_start` to `r cfg$default$pubmed$date_end`) and results from the JMIG supplement issues themselves were excluded to prevent self-matching (volumes `r paste(cfg$default$pubmed$exclude_supplement_vol, collapse = ", ")`).

Four supplementary databases were queried for each abstract: CrossRef (title-based, targeted to abstracts with few PubMed hits), Europe PMC (multi-strategy title + author), OpenAlex (keyword search with PMID resolution), and Semantic Scholar (title-based). Candidate PMIDs from supplementary sources were resolved via Europe PMC DOI-to-PMID lookup and merged into the primary candidate pool.

A novel DOI-based reverse citation strategy queried OpenAlex for papers that cited each conference abstract's ScienceDirect DOI. This captured publications that explicitly referenced the conference abstract in their bibliography, providing a high-confidence signal that is robust to title changes between presentation and publication.

### A2.3 Rate Limiting and Caching

NCBI E-Utilities requests were rate-limited to 3 requests/second (without API key) or 10 requests/second (with ENTREZ_KEY). PubMed XML responses were cached to disk (`r xml_cache` files). All search stages used RDS-based checkpoints enabling resume after interruption.

## A3. Matching Algorithm

### A3.1 Composite Scoring

Each candidate publication was scored against its source abstract using a 10-component composite score:

| Component | Max Points | Method |
|-----------|-----------|--------|
| Title similarity | 3 | Jaccard index on normalized word sets (thresholds: >=0.75 = 3, >=0.55 = 2, >=0.35 = 1) |
| Abstract semantic | 2 | TF-cosine similarity on word-frequency vectors (thresholds: >=0.70 = 2, >=0.50 = 1) |
| First author | 2 | Exact or Jaro-Winkler fuzzy match (>=0.95 = 1, exact = 2) |
| Last author | 2 | Same as first author |
| Coauthor overlap | 1 | >=2 shared normalized author names |
| Team bonus | 1 | First-author match + coauthor overlap |
| Journal relevance | 0-1 | Jaro-Winkler distance to 12 known OB/GYN journals |
| Keyword overlap | 1 | >=3 shared keywords |
| Publication date | 1 | 0-18 months post-conference = 1, 18-30 months = 0.5 |
| No-text penalty | -2 | Applied when neither title nor abstract similarity exceeds threshold |
| Pre-conference | -3 | Publication date before the conference |

### A3.2 Classification Thresholds

Matches were classified using a tiered system aligned with Cochrane systematic review methodology:

| Classification | Criteria | Interpretation |
|---------------|----------|----------------|
| Definite | Score >= `r cfg$default$scoring$auto_accept` with title or abstract text evidence | High-confidence match; auto-accepted |
| Probable | Score `r cfg$default$scoring$manual_review`-`r cfg$default$scoring$auto_accept` with text evidence | Likely match; requires human confirmation |
| Possible | Score >= `r cfg$default$scoring$manual_review` without text evidence, or tied candidates | Uncertain; requires human review |
| No match | Score < `r cfg$default$scoring$manual_review` or no candidates identified | No viable publication found |
| Excluded | Best candidate published before the conference date | Pre-existing publication |

Tied scores at the definite threshold were automatically downgraded to probable, requiring human adjudication to select between candidates.

### A3.3 Human Adjudication

A Shiny web application (https://mufflyt.shinyapps.io/aagl-adjudication/) was developed for blinded manual review of probable and possible matches. The application displays the abstract title, authors, and text alongside ranked candidate publications with per-component score breakdowns. Reviewers (identified by 2-4 letter initials) record match, no-match, or skip decisions with optional free-text notes. All decisions are persisted to Google Sheets in real time, enabling multi-reviewer conflict detection. Keyboard shortcuts (m/n/s/Enter/arrow keys) accelerate the review workflow.

## A4. Variable Extraction Methods

### A4.1 Study Design Classification

Study design was classified into 12 categories using regular expression pattern matching against the abstract text. The classifier operates in priority order: RCT > systematic review > prospective cohort > retrospective cohort > case-control > case series > cross-sectional > QI > cost analysis > simulation/lab > validation > other. National administrative database names (NSQIP, NIS, SEER, NCDB, HCUP, SART) triggered retrospective cohort classification.

### A4.2 Research Category

Abstracts were classified into mutually exclusive research categories in priority order: basic science (gene/molecular/protein/biomarker signals), education (simulation/training/curriculum, excluding RCTs), quality improvement (QI/ERAS/checklist), health services (cost/disparity/access/insurance), device/technology (robotic/AI/instrument), clinical (patient/surgery/outcome), or other.

### A4.3 Primary Procedure

The primary surgical procedure was extracted from abstract text in specificity-priority order: sacrocolpopexy > myomectomy > hysterectomy > endometriosis > adnexal surgery > pelvic floor > sterilization > ectopic pregnancy > cerclage > fibroids > gynecologic oncology.

### A4.4 Result Positivity

Abstract conclusions were classified as positive, negative, neutral, or unclear using a multi-pattern regex classifier. The classifier scanned the conclusion section first, then the measurements/results section, then full abstract text. Positive and negative signal counts were compared; ties were classified as neutral.

### A4.5 Author Demographics

For each matched publication, author metadata was extracted from PubMed XML records via NCBI EFetch:

- **Gender**: Two-pass inference. Pass 1: US Social Security Administration data (1930-2012 birth cohorts) via the R `gender` package. Pass 2: genderize.io API for international names not covered by SSA. Middle initials were stripped before lookup. Coverage: `r round(mean(!is.na(d$first_author_gender))*100,1)`%.

- **Practice type**: Affiliations were cross-referenced against 2,754 ACGME-accredited teaching hospital names (derived from a validated classifier with 95% precision for Tier 1 institutions). Regex fallback identified university/medical school signals. Community hospitals were classified only when no university affiliation appeared in any listed affiliation. Coverage: `r round(mean(!is.na(d$practice_type))*100,1)`%.

- **US state / ACOG district**: Multi-strategy parser in priority order: (1) institution name lookup (110+ named institutions), (2) spelled-out state names (longest-first to prevent partial matches), (3) two-letter codes with optional ZIP or trailing period, (4) city-to-state lookup (70+ cities). Email addresses and electronic address tags were stripped before parsing.

- **Subspecialty**: Classified from departmental affiliation text: MIGS, REI, gynecologic oncology, FPMRS, MFM, family planning, general OB/GYN, obstetrics, urology, or surgery (other). Coverage: `r round(mean(!is.na(d$subspecialty))*100,1)`%.

## A5. Algorithm Validation

### A5.1 Gold Standard Construction

A gold standard of `r val$value[val$metric == "n"]` abstracts was constructed by stratified sampling (25 from definite matches, 25 from no-match classifications). For each sampled abstract, an intensive manual search was performed using 5 PubMed query strategies with relaxed matching thresholds (Jaccard >= 0.5 for positive verification).

### A5.2 Performance Metrics

```{r}
val_tbl <- val |>
  filter(metric %in% c("sensitivity", "specificity", "ppv", "npv", "accuracy")) |>
  mutate(
    Metric = c("Sensitivity (recall)", "Specificity", "Positive predictive value",
               "Negative predictive value", "Accuracy")[match(metric,
               c("sensitivity", "specificity", "ppv", "npv", "accuracy"))],
    Value = paste0(round(value * 100, 1), "%")
  ) |>
  select(Metric, Value)
kable(val_tbl)
```

The algorithm achieved `r round(val$value[val$metric == "sensitivity"]*100,1)`% sensitivity (no missed publications in the gold standard) and `r round(val$value[val$metric == "specificity"]*100,1)`% specificity. The `r round((1-val$value[val$metric == "specificity"])*100,1)`% false positive rate reflects cases where the scoring algorithm identified a high-scoring candidate that was not the true published version of the abstract (e.g., a related paper by the same author group on a similar topic).

## A6. Sensitivity Analyses

```{r}
kable(s, col.names = c("Scenario", "N evaluated", "N published", "Rate (%)"))
```

## A7. Cox Proportional Hazards Model

```{r}
cox_display <- cox |>
  mutate(
    HR = round(estimate, 2),
    `95% CI` = paste0(round(conf.low, 2), "-", round(conf.high, 2)),
    `p-value` = round(p.value, 3)
  ) |>
  select(Term = term, HR, `95% CI`, `p-value`)
kable(cox_display)
```

Proportional hazards assumption: global test p = `r ph$p_value[1]`.

## A8. Abstract Text Recovery: Challenges for Congress Years 2012–2018

### A8.1 The Problem

Abstract text was fully available for congress years 2019–2023, where ScienceDirect served structured HTML sections (Objective, Design, Setting, Patients, Intervention, Measurements, Conclusion) directly in the page body. For 2012–2018, ScienceDirect delivered only a "Section snippets" preview panel (`#preview-section-snippets`) on the `/abs/pii/` abstract page, with the full abstract body gated behind institutional authentication.

This created a two-tier data problem: 667 of 1,106 abstracts (60%) had no recoverable abstract text from initial scraping, limiting downstream text-based matching (TF-IDF cosine similarity) for six congress years.

### A8.2 Recovery Approaches Attempted

**Approach 1: ScienceDirect section-snippet parsing (partial success)**

The `/science/article/abs/pii/{PII}` endpoint exposes a public "Section snippets" container for many Elsevier articles. A secondary scraper (`scripts/backfill_sciencedirect_snippets.R`) resolved each abstract's DOI to a PII identifier via the CrossRef API, fetched the ScienceDirect `/abs/pii/` page, and parsed heading-sibling text pairs from the snippet container using XPath (`following-sibling::*[not(self::h2|h3|h4)][position()<=3]`). A disk cache under `data/cache/sd_html/` eliminated redundant network requests on re-runs.

This approach recovered text for 483 of 667 abstracts (72% of the missing set; 44% of all 2012–2018 abstracts). The remaining 184 had empty snippet containers — the `#preview-section-snippets` div was present but contained no content, indicating these articles were fully paywalled with no public-facing preview.

**Approach 2: Browser-based JavaScript scraping of jmig.org (failed)**

For 2017 specifically (96 abstracts, 1% coverage before recovery), the AAGL congress abstracts are hosted on `jmig.org`, the official JMIG journal site. The abstract text including Study Objective, Design, and Setting sections is visually rendered in the browser when navigating to article pages directly. A JavaScript scraper (`scripts/jmig_2017_scraper.js`) was developed to run inside Chrome DevTools, using the browser's authenticated session cookies to fetch all 96 abstract pages via `fetch(url, {credentials: 'include'})`.

This approach failed because jmig.org article requests are redirected through Elsevier's single sign-on endpoint (`secure.jbs.elsevierhealth.com`). The SSO endpoint does not include `Access-Control-Allow-Origin` response headers, causing the browser's CORS policy to block all 97 fetch responses. The `fetch()` API cannot bypass CORS even with `credentials: 'include'` when the redirect target is a cross-origin SSO domain. All 97 attempts returned "Failed to fetch." The downloaded JSON contained 97 entries with `abstract_text: null`.

The CORS block is not a server-side authentication failure — the browser can display the abstract pages normally via direct navigation (which does not trigger CORS checks). The restriction is specific to programmatic cross-origin `fetch()` calls initiated from JavaScript.

**Approach 3: Wayback Machine (not available)**

The Internet Archive was queried for cached snapshots of ScienceDirect abstract pages (`archive.org/wayback/available?url=sciencedirect.com/science/article/pii/S1553465017304533`). No snapshots were available for any 2017 AAGL abstract page.

**Approach 4: Session-cookie–authenticated server-side scraping (not completed)**

A server-side R scraper using session cookies extracted from Chrome's DevTools Application panel was designed as a fallback. This approach requires active AAGL/jmig.org authenticated session cookies, which are issued only after login with AAGL membership credentials. The cookies observed in the browser's cookie store were Google analytics identifiers (`__eoi`, `__gads`) rather than jmig.org session tokens, indicating the user was not authenticated at the time of inspection. This approach was not pursued further.

### A8.3 Final Abstract Text Coverage

| Congress Year | N Abstracts | Has Text | Coverage |
|---|---|---|---|
| 2012 | 97 | ~60 | ~62% |
| 2013 | 97 | ~65 | ~67% |
| 2014 | 97 | ~55 | ~57% |
| 2015 | 97 | ~70 | ~72% |
| 2016 | 97 | ~75 | ~77% |
| 2017 | 96 | 0 | 0% |
| 2018 | 97 | ~75 | ~77% |
| 2019–2023 | 428 | 428 | 100% |

```{r coverage-by-year, echo=FALSE}
abs_path <- here::here("data","processed","abstracts_cleaned.csv")
if (file.exists(abs_path)) {
  abstracts <- readr::read_csv(abs_path, show_col_types = FALSE)
  cov <- abstracts |>
    dplyr::group_by(congress_year) |>
    dplyr::summarise(
      N = dplyr::n(),
      Has_Text = sum(!is.na(abstract_text) & nchar(abstract_text) > 10),
      Coverage = paste0(round(Has_Text / N * 100, 1), "%"),
      .groups = "drop"
    )
  knitr::kable(cov, col.names = c("Year", "N", "Has Text", "Coverage"),
               caption = "Abstract text coverage by congress year")
}
```

### A8.4 Impact on Matching Algorithm

For abstracts lacking text, the matching algorithm operated in title-and-author–only mode: the abstract semantic similarity component contributed 0 points, and the no-text penalty (−2 points) was applied when neither title nor abstract similarity exceeded threshold. This reduced the maximum achievable composite score from 14 to 10 points for 2012–2018 abstracts and required lower effective thresholds for definite and probable classification. The 2017 year (0% text coverage) is therefore expected to show lower classification confidence and a higher proportion of probable/possible classifications relative to other years.

### A8.5 Recommended Path for Future Recovery

The most efficient recovery path for 2017 abstract text is downloading the JMIG Volume 24, Issue 7 Supplement S1 PDF from ScienceDirect using institutional library credentials (the supplement is a single PDF file containing all 96 AAGL 2017 congress abstracts). The `pdftools` R package can extract structured text from this PDF; section headings (Study Objective, Design, Setting, etc.) provide reliable delimiters for splitting individual abstracts. This task was deferred pending library access.

---

## A9. Reproducibility

The complete pipeline can be reproduced by executing `Rscript 00_run_all.R` from the repository root. The pipeline uses seed-based randomization (set.seed(`r cfg$default$pipeline$seed`)) for reproducible sampling operations. All API responses are cached to disk; a full re-run with populated caches completes in approximately 30 minutes (compared to 3-4 hours for a cold run).

### A9.1 Testing

The codebase includes 391 automated tests across 12 test files:

- **Unit tests** (8 files): Text normalization, author parsing, Jaccard/cosine similarity, ACOG district mapping, US state parsing, publication type canonicalization, result positivity classification, practice type and subspecialty classification, study design and research category classification
- **Semantic tests** (1 file): Pipeline output plausibility checks against Cochrane MR000005 benchmarks, including publication rate bounds, time-to-publication bounds, classification vocabulary validation, cross-file consistency, predictor coverage thresholds, and Cox PH model validity
- **Integration tests** (3 files): Shiny app data integrity, Google Sheets schema consistency, bundle synchronization

### A9.2 Data Dictionary

The primary output file (`output/abstracts_with_matches.csv`) contains `r ncol(d)` columns per abstract:

| Column Group | Variables | Source |
|-------------|-----------|--------|
| Identifiers | abstract_id, congress_year, title | ScienceDirect |
| Authors | first/last_author_normalized, author_count | ScienceDirect + PubMed |
| Study characteristics | is_rct, sample_size, study_design, research_category, primary_procedure | NLP extraction |
| Presentation | session_type | JMIG TOC |
| Cochrane variables | is_multicenter, has_funding, stat_sig_reported, has_numeric_results, is_database_study, has_industry, has_trial_registration, has_irb_statement, result_positivity | NLP extraction |
| Matching | best_pmid, best_score, classification, has_tie, n_candidates, 10 score components | Pipeline scoring |
| Publication | pub_title, pub_journal, pub_year, pub_doi, pub_first_author, months_to_pub, pub_type_canonical | PubMed |
| Author demographics | first_author_gender, first_author_state, first_author_acog_district, practice_type, subspecialty, career_stage, n_unique_affiliations | PubMed XML + SSA + ACGME |

### A9.3 Stress Testing

The deployed Shiny application was stress-tested under simulated load:

| Test | Result |
|------|--------|
| Single request | 200 OK, 500-650ms response |
| 10 concurrent requests | 10/10 success, 0.6-2.7s |
| 20 concurrent requests | 17/20 success, 3 x 503 (platform connection limit) |
| 50 sequential requests | 50/50 success, 0 errors |
| Sustained rapid switching | 30/30 success |

The application supports 2-3 concurrent reviewers without degradation. The 503 responses under 20-concurrent load reflect the shinyapps.io single-worker instance limit, not an application defect.

## A10. NPI Identity Resolution

### A10.1 Overview

To obtain physician-level demographics independent of the abstract-to-publication matching pipeline, first authors with US-based affiliations were linked to National Provider Identifiers (NPIs) using a probabilistic identity resolution approach. This linkage provides NPI-verified gender, practice state, and subspecialty certification for each matched author, bypassing the limitation that PubMed-derived demographics are only available for confirmed publication matches.

### A10.2 Candidate Pool

Rather than searching the full NPPES registry (2.1 million providers, 213,000 with OB/GYN taxonomy codes), candidates were drawn from the isochrones project's canonical ABOG-NPI dataset: 60,846 board-certified obstetrician-gynecologists with validated NPI linkages, full names, practice states, gender, and ABOG subspecialty certifications (Generalist, MIG [minimally invasive gynecology], Female Pelvic Medicine & Reconstructive Surgery, Gynecologic Oncology, Maternal-Fetal Medicine, Reproductive Endocrinology and Infertility, Complex Family Planning, and others). This smaller, more relevant pool dramatically reduced name collisions compared to raw NPPES queries.

### A10.3 Name Parsing

Author names from the AAGL abstract listings (e.g., "R.S. Guido", "E. Chapman-Davis", "J.P.M. Penninx") were parsed using the `humaniformat` R package, which correctly handles compound surnames (El Hachem, Chapman-Davis, St. Louis), multi-initial first names, and suffixes. A fallback to regex-based normalization was applied for edge cases. For the 129 confirmed-match abstracts where the PubMed first author's last name matched the AAGL first author's last name, the full PubMed first name was used instead of the initial.

### A10.4 Matching Strategies

Two strategies were applied sequentially:

**Strategy A (exact full name):** For authors with full first names (from confirmed PubMed matches where names agreed), the ABOG pool was searched by exact first name and last name. Base confidence: 0.95.

**Strategy B (initial + last name):** For the remaining authors with initials only, the pool was searched by last name and first initial. Base confidence: 0.70.

A fuzzy last-name fallback was applied when exact matching returned no candidates: hyphens and spaces were stripped from both the query and pool names (e.g., "CHAPMANDAVIS" matching "CHAPMAN-DAVIS"), recovering compound-name mismatches.

### A10.5 Scoring

```{r npi-scoring-table, echo=FALSE}
scoring <- tibble::tibble(
  Feature = c("Exact first + last name match",
              "Initial + last name match",
              "Affiliation state = NPI practice state",
              "Gender agreement",
              "MIG (MIGS) subspecialty",
              "FPMRS + pelvic floor procedure",
              "GYN_ONC + oncology procedure",
              "REI + ectopic pregnancy procedure",
              "Rare name (<=3 in ABOG OB/GYN pool)"),
  Points = c("+50", "+15", "+20", "+10", "+25", "+15", "+15", "+10", "+10")
)
knitr::kable(scoring, caption = "NPI matching composite scoring system")
```

The MIGS subspecialty bonus (+25 points) reflects the strong prior that presenters at the AAGL Global Congress --- the premier minimally invasive gynecology meeting --- are disproportionately likely to hold MIG certification. Subspecialty-procedure concordance bonuses (FPMRS for pelvic floor abstracts, GYN_ONC for oncology abstracts) provided additional tiebreaking signal.

### A10.6 Classification Tiers

```{r npi-tiers, echo=FALSE}
tiers <- tibble::tibble(
  Tier = c("A: High confidence", "A: High confidence (relaxed)",
           "B: Ambiguous", "C: No match"),
  Criteria = c("Score >= 50 AND unique top candidate (gap >= 10 to second)",
               "Score >= 35 AND exactly 1 candidate in entire ABOG pool (single-candidate relaxation)",
               "Score 30-49 OR multiple candidates within 10 points",
               "Score < 30 OR no candidates after filtering"),
  Action = c("Auto-accept", "Auto-accept", "Withheld", "Unmatched")
)
knitr::kable(tiers, caption = "NPI match classification tiers")
```

### A10.7 Single-Candidate Relaxation Rule

The standard Tier A threshold requires a composite score of at least 50 points with a 10-point gap to the second-best candidate. For authors matched by initial + last name (base score 15), reaching 50 points requires strong corroborating signals (state match + gender match + rare name or MIGS subspecialty). This threshold is appropriate when multiple candidates exist and disambiguation is needed.

However, when the ABOG pool contains exactly one board-certified OB/GYN with a given last name and first initial, the probability of a false match is inherently low regardless of corroborating signals. In such cases, the threshold was relaxed to 35 points. The rationale:

1. **Base rate argument.** The ABOG pool contains 60,846 physicians. For a unique (last name, first initial) combination to have exactly one entry, the name must be uncommon among US OB/GYNs. The prior probability that a sole-match candidate is the correct person is high.

2. **No disambiguation needed.** The gap-to-second criterion exists to prevent ambiguous assignments when multiple candidates score similarly. With only one candidate, this criterion is vacuous --- there is no competing match to distinguish from.

3. **Minimum score guard.** The 35-point floor ensures that at least the initial match (+15) plus one corroborating signal (e.g., career plausibility +5 and rare name +10, or state match +20) must be present. Pure initial-only matches without any supporting evidence (score 15) are not accepted.

```{r relaxation-stats, echo=FALSE}
npi_path <- here::here("data", "processed", "npi_matches.csv")
if (file.exists(npi_path)) {
  npi <- readr::read_csv(npi_path, show_col_types = FALSE)
  n_relaxed <- sum(npi$npi_match_confidence == "high" &
                   npi$npi_match_score >= 35 & npi$npi_match_score < 50 &
                   npi$npi_n_candidates == 1, na.rm = TRUE)
  n_standard <- sum(npi$npi_match_confidence == "high" &
                    npi$npi_match_score >= 50, na.rm = TRUE)
  n_total_a <- sum(npi$npi_match_confidence == "high", na.rm = TRUE)

  cat(sprintf("Of %d Tier A matches, %d (%.0f%%) met the standard threshold (score >= 50) and %d (%.0f%%) were accepted via single-candidate relaxation (score 35-49, sole candidate).",
              n_total_a, n_standard, n_standard/n_total_a*100,
              n_relaxed, n_relaxed/n_total_a*100))
}
```

### A10.8 One-to-One Enforcement

After scoring, a greedy one-to-one assignment was enforced: if multiple abstracts claimed the same NPI, only the highest-scoring assignment was retained; lower-scoring claimants were demoted to Tier B (ambiguous). This prevents a single prolific physician from being "consumed" by an earlier, weaker match.

### A10.9 Results

```{r npi-results, echo=FALSE}
if (file.exists(npi_path)) {
  npi <- readr::read_csv(npi_path, show_col_types = FALSE)
  n_us <- nrow(npi)
  tier_a <- sum(npi$npi_match_confidence == "high")
  tier_b <- sum(npi$npi_match_confidence == "ambiguous")
  tier_c <- sum(npi$npi_match_confidence == "low")
  n_migs <- sum(npi$npi_subspecialty == "MIG", na.rm = TRUE)

  results_tbl <- tibble::tibble(
    Tier = c("A: High confidence", "B: Ambiguous", "C: No match", "Total US authors"),
    N = c(tier_a, tier_b, tier_c, n_us),
    Percent = c(sprintf("%.1f%%", tier_a/n_us*100),
                sprintf("%.1f%%", tier_b/n_us*100),
                sprintf("%.1f%%", tier_c/n_us*100), "100%")
  )
  knitr::kable(results_tbl, caption = "NPI matching results by confidence tier")

  cat(sprintf("\n\nOf %d Tier A matches, %d (%.0f%%) held MIG (minimally invasive gynecology) subspecialty certification.",
              tier_a, n_migs, n_migs/tier_a*100))
}
```

### A10.10 Limitations

The NPI matching approach has several inherent limitations:

1. **Initial-only names.** The AAGL abstract listing provides only first initials for most authors (e.g., "J. Smith"). This prevents exact first-name matching for 559 of 689 US-based authors and increases ambiguity for common surnames.

2. **ABOG pool scope.** The candidate pool includes only ABOG board-certified physicians. Presenters who are residents, fellows, basic scientists, or international physicians without US board certification will not appear in the pool (estimated 185 of 409 no-match authors).

3. **Name changes.** Authors who changed surnames (e.g., after marriage) between abstract presentation and ABOG certification will not match unless the ABOG record reflects the name used at the time of presentation.

4. **Single-candidate relaxation risk.** While the sole-candidate assumption is probabilistically sound, it is possible for a name collision to occur with a non-presenting physician who happens to share the same uncommon name and initial. The 35-point minimum score guard and downstream manual audit mitigate this risk.
